MCC Models

### 2019-07-23 papers/full_paper/SI_appendix.Rmd
add note and speaker math equation

>>>>

TO CREATE S(u | r), WE NEED TO HAVE THE INFORMATIVITY OF EACH OF THE 4 UTTERANCES. PASSING THE INFORMATIVITY THROUGH THE SOFT-MAX (speaker optimality) creates an "unnormalized" probability, which we then turn into a real probability by dividing by the sum of all the unnormalized probabilities of each utterance.

$$
P_{S_1}(u|r) = \frac{exp(\alpha Informativity(u;r))}{\sum_{u'} exp(\alpha Informativity(u';r))}
$$
